%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

        %---------------------------------------------------------
	\cventry
	{Software Engineer Intern}
	{\href{https://www.linkedin.com/company/aldeiaweb/}{Aldeiaweb}}
	{Goiás, Brazil}
	{Aug. 2025 - Present}
	{
		\begin{cvitems}
        \item {\textbf{Developed} a \textbf{SaaS} platform using \textbf{Laravel}, implementing a single-database multi-tenancy architecture with data isolation and privacy guarantees.}
        \item {\textbf{Engineered statistical modules} and dynamic dashboards to provide real-time data insights and performance metrics for end-users.}
        \item {\textbf{Refactored core system modules} to improve code maintainability and scalability, applying \textbf{Design Patterns} to ensure a high-quality codebase.}
        \item {\textbf{Optimized database performance} and backend logic to handle complex data queries, ensuring seamless user experience and data integrity.}        
        \end{cvitems}
	}
    \vspace{.5cm}
        
	%---------------------------------------------------------
	\cventry
	{Backend Developer Intern}
	{\href{https://www.linkedin.com/company/rgm-tecnologia-inteligência-e-processos/}{RGM}}
	{São Paulo, Brazil}
	{Jan. 2025 - Jul. 2025}
	{
		\begin{cvitems}
        \item {\textbf{Standardized the UI/UX} across 3 core corporate modules (over 150 applications), resulting in a \textbf{40\% improvement} in user experience and reduced onboarding time.}
        \item {\textbf{Developed dynamic reporting systems} in PHP for automated data consolidation, enhancing managerial decision-making processes.}
        \item {\textbf{Built a centralized Cookie Management API} using \textbf{Laravel}, ensuring LGPD (General Data Protection Law) compliance and improving data architecture.}
        \item {\textbf{Collaborated in an Agile environment (Scrum)}, actively participating in sprints and daily meetings to ensure continuous delivery and software quality.}
        % \item {Enabled the organization to address key questions, such as the total number of apps, year-over-year growth, app installation locations, and app lifecycle events, fostering \textbf{data-driven} decision-making within the product team.}
		\end{cvitems}
	}
    \vspace{.5cm}
		
	%---------------------------------------------------------
	% \cventry
	% {Software Engineer} % Job title
	% {\href{https://www.linkedin.com/company/vtex/}{VTEX}} % Organization
	% {Rio de Janeiro, Brazil} % Location
	% {Dec. 2020 - Dec. 2021} % Date(s)
	% {
	% 	\begin{cvitems}
	% 		\item {Developed a \textbf{micro-service} that offers scheduling of HTTP requests and queries, focusing on \textbf{efficiency} and maintainability.}
	% 		\item {Deployed to production, resulting in \textbf{75\% financial savings} over the previous scheduling service. Helped \textbf{other teams} and services migrate to the new Scheduler.}
	% 		\item {Identified and implemented \textbf{performance improvements} in request handling,  improving maximum processing capacity per minute by \textbf{3000\%}.}
	% 	\end{cvitems}
	% }
		
	%---------------------------------------------------------
\end{cventries}