%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Student \href{https://www.linkedin.com/company/cnpq---mct/}{(PIBIC/CNPq)}} % Affiliation/role
    {\href{https://www.linkedin.com/school/ifpiaui/}{IFPI}} % Organization/group
    {Parnaíba, Piauí, Brazil} % Location
    {Oct. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\textbf{Developing and implementing} a responsive, open-source mobile system for archaeological data cataloging and management.}
        \item {Designing the system to streamline data collection from excavations, ensuring compliance with \textbf{IPHAN (National Institute of Historic and Artistic Heritage)} regulations.}
        \item {Optimizing archaeological workflows by transitioning from manual and desktop-based tools to a \textbf{high-efficiency mobile solution}.}
        \item {Utilizing \textbf{Flutter and Dart} to build a cross-platform application focused on accessibility and data integrity in the field.}
        \end{cvitems}
    }
    \vspace{.5cm}

%---------------------------------------------------------

  % \cventry
  %   {Founder and Professor} % Affiliation/role
  %   {\href{https://www.linkedin.com/school/oficialufpi/}{UFPI} Competitive Programming Study Group} % Organization/group
  %   {Teresina, Piauí, Brazil} % Location
  %   {Mar. 2021 - Present} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {\textbf{Founded and taught} several topics covering areas such as Graph Theory, Dynamic Programming, Algorithms and Data Structures.}
  %       \item {Several students from my course \textbf{achieved} notable success, earning medals, reaching competition finals, and receiving job offers.}
  %       \item {Instigated a \textbf{competitive programming culture} at my university, empowering students to collaborate independently.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------


\begin{comment}

  \cventry
    {Undergraduate Research Student} % Affiliation/role
    {\href{https://www.linkedin.com/school/oficialufpi/}{UFPI}} % Organization/group
    {Brazil} % Location
    {Sep. 2020 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\textbf{Mined software repositories}, extracting and analyzing development metrics, including the \textbf{Truck Factor}, to assess project robustness.}
        \item {Developed an API to automate the \textbf{visualization of metrics}, pinpointing outliers and calculating limits based on the extracted data.}
      \end{cvitems}
    }
\end{comment}


%---------------------------------------------------------
\end{cventries}
